---
title: "Weight of Fish"
author: "America Olivo"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight



## Perch

```{r}
Fish <- read.csv("Fish.csv")

Perch <- filter(Fish, Species=="Perch")

Perch <- select (Perch,-Species)
```



```{r}
basicNN <- ggplot(Perch,aes(y=Weight, x=Length3)) 
basicNN + geom_point()+ geom_lm()
```




### Best Models




### Best Two regressor model


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

The two best regressive models are Height and Weight because their adjusted R^2 is closer to 1 (0.9400).

```{r}
perchmodel <- lm (Weight~ Height + Width, data=Perch)
summary.lm(perchmodel)
```


```{r}
pmodel <- lm (Weight~ Height + Width + Length1+ Length2+ Length3, data=Perch)
summary.lm(pmodel)
```

We used models that gave us our residual standard error and adjusted r^2 in order to double check our first claim. Since the adjusted r^2 is closer to 1, it proves that these models are the best fit. Our standard error is at its lowest with Height and Weight. 

## Bream

```{r}
Fish <- read.csv("Fish.csv")

Bream <- filter(Fish, Species =="Perch")

Bream <- select (Bream,-Species)
```

### Best Models

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
The best two regressive models are Length 1, Height, and Width then Length 2 and Height because they are closest to 1 which means its more accurate than the rest. 

```{r}
breammodel <- lm (Weight~ Height + Width, data=Bream)
summary.lm(breammodel)
```

```{r}
model3 <- lm (Weight~ Height + Width + Length1+ Length2+ Length3, data=Bream)
summary.lm(model3)
```
This model shows us how accurate our two regressive models because they are closer to one with the adjusted r^2. 


## Roach

```{r}
Fish <- read.csv("Fish.csv")
Roach <- filter(Fish, Species=="Roach")
Roach <- select (Roach,-Species)
```


### Best Model

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```


Our best regression model is Length3 and width because the adjusted r^2 is the highest one compared to the others. Since its closer to one its more accurate.


```{r}
roachmodel <- lm (Weight~ Length3 + Width, data=Roach)
summary.lm(roachmodel)
```


## Final Summary Statements

The fish species Bream has a mean weight of 617.8 which is 1.6x as big as Perch. which is 382.2. Roach has a mean weight that is twice as small(152.0) as Perch. Half as big as the Perch species. Bream is the heaviest fish twice as heavy as Perch. 
0.94 perch adjusted r^2, standard deviation is higher than all fishes at 347.61. 
0.93 bream adjusted r^2, standard deviation is lower than perch, 347.6, but still has a higher number than roach. 
Perch has a Residual standard error of 85.17 which indicates that the data is not as close as Bream as its Residual standard error is 53.1. The lower the Residual standard error and the higher the r^2 shows how accurate the species Bream was. 

