---
title: "Weight of Fish"
author: "America Olivo"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight



## Perch

```{r}
Fish <- read.csv("Fish.csv")
Perch <- filter(Fish, Species=="Perch")
Perch <- select (Perch,-Species)
```


### Best Models


### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

The two best regressive models are Height and Weight because their adjusted R^2 is closer to 1 (0.9400).

```{r}
perchmodel <- lm (Weight~ Height + Width, data=Perch)
summary.lm(perchmodel)
```


```{r}
pmodel <- lm (Weight~ Height + Width + Length1+ Length2+ Length3, data=Perch)
summary.lm(pmodel)
```

We used models that gave us our residual standard error and adjusted r^2 in order to double check our first claim. Since the adjusted r^2 is closer to 1, it proves that these models are the best fit. Our standard error is at its lowest with Height and Weight. 

## Bream

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements